Four reasons your build is slow

### 2019-01-17 paper.tex
Citations.
They finally told us how to format.

\documentclass[sigplan,10pt,review,authorversion]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}

\citestyle{acmnumeric}

@@

Some projects may exhibit ample potential parallelism but may not achieve that potential
parallelism in practice.  LLVM \cite{} is the largest
project we analysed, with a calculated work of approximately 12584 seconds, or 3.5 hours.
With a predicted span of 305 seconds, or 5 minutes, LLVM has a parallelism of about 41.
These calculations where made from a build of LLVM that was run without strace.

@@

>>>>

\documentclass[sigconf,10pt,review,authorversion]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
\usepackage{geometry}
\geometry{reset, twoside=true, head=13pt,
     paperwidth=8.5in, paperheight=11in,
     includeheadfoot, columnsep=2pc,
     top=57pt, bottom=73pt, inner=72pt, outer=72pt,
     marginparwidth=2pc,heightrounded
     }
\citestyle{acmnumeric}

@@

Some projects may exhibit ample potential parallelism but may not achieve that potential
parallelism in practice.  LLVM~\citep{LLVM:CGO04} is the largest
project we analysed, with a calculated work of approximately 12584 seconds, or 3.5 hours.
With a predicted span of 305 seconds, or 5 minutes, LLVM has a parallelism of about 41.
These calculations where made from a build of LLVM that was run without strace.

@@

\bibliographystyle{ACM-Reference-Format} 
\bibliography{citations}
\balance
